\documentclass[12pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{daves,fancyhdr,natbib,graphicx,dcolumn,amsmath,lastpage,url}
\usepackage{amsmath,amssymb,epstopdf,longtable}
\usepackage{paralist} 
\usepackage[final]{pdfpages}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\pagestyle{fancy}
\lhead{CE 4200 -- Professional Engineering Practice Issue}
\rhead{SPRING 2025}
\lfoot{EXERCISE 1.2}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\renewcommand\headrulewidth{0pt}

\begin{document}

\begin{center}
{\textbf{{ CE 4200 -- Professional Engineering Practice Issues} }}
\end{center}

\section*{\small{Exercise 1.2}} 
\emph{Understanding the ASCE CEBOK3}


\section*{\small{Purpose}} 
The purpose of this learning exercise is to help you 
\begin{itemize}
\item Access to the class website and upload completed exercises as .PDF files.
\item Demonstrate comprehension – in both breadth and detail – the
relationship between civil engineering skills/ outcomes identified in the ASCE Body of Knowledge Third
Edition (CEBOK3) and your program of study represented in the undergraduate civil engineering
curriculum at Texas Tech University.
\end{itemize}

\section*{\small{Exercise}}
\begin{enumerate}
    \item Familiarize yourself with the source materials provided on the class website, Blackboard, and the internet These include:
    \begin{itemize}
        \item Civil Engineering Degree Program, Texas Tech University (use the most current copy you can find)
        \item Course descriptions, current Undergraduate and Graduate Course Catalog
        \item ASCE Body of Knowledge, Third Edition
        \item This assignment
    \end{itemize}

    \item The focus of the assignment is a 1-page form (\texttt{.xlsx} link on Blackboard) entitled “Compare CE Degree Program vs. ASCE Body of Knowledge Outcomes”. This form identifies all courses in the undergraduate civil engineering program (rows) and all 21 outcomes in the CEBOK3 (columns). You will use this form two times.
    \begin{itemize}
        \item First, identify all CEBOK3 outcomes that you think are associated with each course in the curriculum (comprehensive)
        \item Second, identify the primary CEBOK3 outcome associated with each course in the curriculum (select only ONE).
    \end{itemize}
    \item Having carefully completed both elements of Part 2, write a one-page narrative wherein you address the following questions:
    \begin{itemize}
        \item From your comprehensive and selective analysis, state whether you think the CE curriculum
adequately and appropriately covers all CEBOK3 outcomes. Are there are any deficiencies
and/or unnecessary duplication? Explain your answer.
        \item You may have noticed the total credit hours in the curriculum is 129. This number is fixed and
cannot change. Do you agree or disagree with 129 hours? Justify your answer.
        \item Can you do better? Assume the curriculum would benefit from refinement to more fully achieve the CEBOK3 outcomes. Keeping in mind the zero-sum nature of the curriculum; that is, the course credit hour total must remain constant at 129 hours:
        \begin{enumerate}[a)]
            \item What course(s) if any would you delete and likewise, what would you add in its place?
            \item What course(s) should be added and likewise, what would you delete to make room?
        \end{enumerate}
    \end{itemize}
This part of the assignment should be typed, 12-pt, double space, 1-inch margin. One page maximum
\end{enumerate}

\section*{\small{Deliverables}}
\begin{enumerate}
    \item Compare CE Degree Program vs. ASCE Body of Knowledge Outcomes (comprehensive) (submit as PDF)
    \item Compare CE Degree Program vs. ASCE Body of Knowledge Outcomes (primary single outcome per course) (submit as PDF)
    \item Narrative report addressing questions above \textbf{Length}: 250-300 words (roughly 1 pages) (submit as PDF)
\end{enumerate}

\section*{\small{Evaluation Criteria\footnote{The narrative report will be evaluated by a narrow domain AI agent, with instructions to identify answers to the listed items.  The AI agent will also have access to BOK3 as well as a current Dynamic Enrollment Management Plan.}}}
\begin{itemize}
    \item Compare CE Degree Program vs. ASCE Body of Knowledge Outcomes (comprehensive) \textbf{Completion}
    \item Compare CE Degree Program vs. ASCE Body of Knowledge Outcomes (primary single outcome per course) \textbf{Completion}
    \item Narrative report \textbf{Explicit answers to the questions; suitable grammar to satisfy a computer agent}
\end{itemize}

\section*{\small{Submission Requirements}}
\begin{itemize}
    \item \textbf{Format}: Narrative portion, typed, double-spaced, 12-point Times New Roman font, 1-inch margins.
    \item \textbf{Submission}: Upload your contents as a PDF to the course’s online portal (Blackboard).
\end{itemize}



\end{document}

