\documentclass[12pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{daves,fancyhdr,natbib,graphicx,dcolumn,amsmath,lastpage,xurl}
\usepackage{amsmath,amssymb,epstopdf,longtable}
\usepackage[final]{pdfpages}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\pagestyle{fancy}
\lhead{CE 4200 -- Professional Practice Issues}
\rhead{FALL 2024}
\lfoot{ES3}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\renewcommand\headrulewidth{0pt}



\begin{document}
\begin{center}
{\textbf{{ CE 4200 Professional Practice Issues} \\ {Exercise Set 3}}}
\end{center}
\section*{\small{Purpose}}
Familiarize yourself with the license process in Texas, the Texas Engineering Practices Act, and perform critical thinking with regards to Texas Licensing and other states.
\section*{\small{Exercises}}
\begin{enumerate}
\item Watch the video on licensing at \url{https://www.nspe.org/resources/licensure/why-get-licensed/professional-engineers-building-career-making-difference}.  How long is the video entitled "Why is the Professional Engineering License Important?"  What are the top 4 reasons in the video and/or on the NSPE website?

\item Download a copy of the current Texas Engineering Practices Act.  Locate in the act the definition of engineering and educational requirements for licensing. Select any other state (or commonwealth nation) and find their engineering practices act.   Locate in the other act the definition of engineering and educational requirements for licensing.  Write a short essay (few paragraphs) where the two definitions are compared and contrasted, are they identical, slightly different etc.   Additionally comment on how these requirements compare to the requirements in the video.

\item Under what conditions can the PE Examination be waived (identify the specific paragraph in the Act as well as the actual wording)?

\item Assume you have a Texas license, what would you have to do to practice in the other state (i.e. read the requirements in the other state for legal practice)?

\item Assume you have a Texas license, what would you have to do to practice in Scotland?

\item What are the meanings of “Comity” and “Reciprocity” in the context of engineering licensure?

\end{enumerate}

\end{document}  