\section*{Bibliography}
This article was written using materials cited in footnotes as well as the following materials

Brown, Jeff. 2004. "Workshop advances global principles of professional conduct" ASCE News November 2004.

Fleddermann, C.B., 1999. Engineering Ethics. Prentice Hall, NJ 135p.

Potter, M.C., 1999. Fundamentals of Engineering (FE Review Book). Great Lakes Press, Okemos, MI. 627p.

Texas Engineering Practices Act (on web - google texas Board of Professional Engineers  for a current copy).

Locke, John. 1689. Two treatises of government   (in public domain).  This document is a likely source of much of Jefferson's thoughts.

Locke, John, 1689. An essay concerning human understanding   (in public domain).

Mill, John Stuart. 1859.  On Liberty (in public domain).

Mill, John Stuart. 1861. Utilitarianism (in public domain).

Kant, Immanuel. 1785.  Grundlegung zur Metaphysik der Sitten (Grounding for the Metaphysics of Morals) (in public domain).

Kant, Immanuel. 1788.  Kritik der practischen Vernunft (Critique of Practical Reason) (in public domain).

Sources for the comics images used are listed below:

http://www.unitedmedia.com/comics/dilbert/  (Source for Dilbert images)

http://www.rhymeswithorange.com/ (Source for Rhymes with Orange images)

http://www.gocomics.com/closetohome/ (Source for Close to Home images)

http://www.kingfeatures.com/features/comics/hagar/about.htm (Source for Hagar the Horrible images)

http://www.gocomics.com/nonsequitur/ (Source for Non Sequitur images)

http://www.creators.com/comics/rubes.html?comicname=rub (Source for Rubes images)

