\section*{Introduction}
Ethics is the study and practice of principles that govern activities between people in their personal and professional lives.  Professional ethics are principles that govern activities between professionals and their clients, customers, and the public.  Engineering ethics includes the general concepts of professional ethics but also includes principles governing activities related to the approval of plans, designs, specifications and requisite qualifications (of engineers).

Ethics and the concern regarding their importance to society have been around as long as there has been society.  Most ethical principles have evolved from centuries of human experience and are common to all cultures.

Examination of the ''definitions'' above contain two important components; 
\begin{enumerate}
\item principles that govern activities provide guidance for how we act.
\item requisite qualifications provide guidance for whom should act.
\end{enumerate}

The remainder of this article discusses some principles relevant to engineering ethics in today's society.  Although the article appears to be authoritative, it is not\footnote{This essay and the presentation contain copyrighted materials, it is the authors' opinion that use of these materials is within the fair-use provision of U.S. Copyright law, however any redistribution of these materials outside the course would materially violate U.S. Copyright law.}.  I am not a licensed lawyer, or credentialed philosopher (although I suppose the Ph.D. might count).  I have tried in good faith to acknowledge where I obtained the thoughts and opinions presented in this article, but few parts are truly my own work.  This article should be read with that understanding; the references to parts of the Texas Engineering Practices Act may have moved around, and the reader is expected to seek out the appropriate sections of the Act to understand the ethical implications expressed in the Act.